---
title: "P8105_hw1_zl3545"
author: "Zeqi Li"
output: github_document
date: "2024-09-19"
---
```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

## Load data set
```{r load_data}
data("penguins",
     package = "palmerpenguins")
```

The "penguins" data set contains a tibble data frame with the following
variables that describe the penguins: `r colnames(penguins)`.

The tibble data frame contains `r nrow(penguins)` rows and `r ncol(penguins)`
columns of data.

The mean flipper length for these penguins is 
`r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

## Plot data
```{r plot_data, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm,
                     y = flipper_length_mm,
                     color = species)) + geom_point()
```

## Save the above scatterplot
```{r save_plot, warning = FALSE, message = FALSE}
ggsave(filename = "flipper_length_vs_bill_length_scatterplot.png")
```

# Problem 2

## Create a data frame
```{r make_df}
df = tibble(sample = rnorm(10),
            pos = sample > 0,
            chr = c('a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'i', 'j'),
            fct = factor(c("L1", "L1", "L1", "L2", "L2", "L2", "L2", "L3", "L3", "L3")))
df
```

## Taking the mean of each variable
```{r avg, collapse = TRUE}
sample_mean = mean(pull(df, sample))
pos_mean = mean(pull(df, pos))
chr_mean = mean(pull(df, chr))
fct_mean = mean(pull(df, fct))
```
The mean of the `sample` variable in this data frame is `r sample_mean`. 
The mean of the `pos` variable in this data frame is `r pos_mean`. We cannot 
take the mean of the `chr` and the `fct` variables because of their data types.

## Converting data types
```{r convert, results = 'hide', warning = FALSE}
as.numeric(pull(df, pos))
as.numeric(pull(df, chr))
as.numeric(pull(df, fct))
```
When we tried to convert the data type of `pos`, `chr`, and `fct` into numerical 
types, only `pos` (a logical variable) and `fct` (a factor variable) were 
successfully converted. 

Logical variables can be converted into numerics based on the rules that 
`TRUE == 1` and `FALSE == 0`, so the numerics `0` and `1` were coerced to `pos` 
when we applied `mean()` and `as.numeric()`.

Factor variables are stored as integers internally, but they typically represent 
categorical data instead of having numerical meanings. When we applied 
`as.numeric()` to `fct`, the internal integers were coerced to `fct`. But 
applying `mean()` on `fct` generated `NA` because R does not automatically 
coerce numerics onto factor variables.

Applying `mean()` and `as.numeric()` on the `chr` variable generated `NA` 
because character variables do not have numerical meanings in R and R cannot 
coerce numerics onto character variables.
